---
title: "Cabbages"
author: "Gianna Chevez"
date: "2/25/25"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We analyzed the variables and identified that we have numerical variables, specifically the amount of vitamin C contained in the two different cultivation methods. These cultivation methods, labeled as C39 and C52, represent the categorical variables.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
plot(VitC~Cult,data=veggy)
```

Upon analyzing the variables, we identified the presence of numerical variables, specifically the amount of vitamin C contained in the two different cultivation methods. These cultivation methods, designated as C39 and C52, represent the categorical variables.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(VitC~Cult,data=veggy)
```

The data indicates that the C52 cultivation method yields higher vitamin C content than C39. The mean for C52 is 64.4, compared to 51.5 for C39, and the median follows a similar pattern (64.5 vs. 51.0). The range for C52 is 47 to 84, while for C39, it is 41 to 68. Quartiles further support this trend: Q1 (58 vs. 46) and Q3 (70.75 vs. 54.75). However, C52 has greater variability (SD: 8.45 vs. 7.12). With 30 samples per group and no missing data, C52 appears to be the better method for maximizing vitamin C content.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
